### 2023-10-29 design/crossbar.tex
Tried to fix cross bar

\subsection{Serialization/Parallelization}
\label{subsec:serpar}

The idea using the system in a serial mode came from \cite{thesisRef}. The principle of this system is to save onChip area by reducing the number of \ac{opAmp} required. Using the system in serial mode, increases the time it takes to compute the output of the the \ac{VMM}. Let's assume a serial size of $n_s\in\mathbb{N}$, the number of \ac{opAmp} and resistor is then divided by $n_s$ at the cost of multipying the computation time by $n_s$.

>>>>

\subsection{Serialization}
\label{subsec:serpar}

This circuit has the option to be serialized with varying degrees. The idea of serializing the circuit came from \cite{thesisRef}. Serializing the circuit reduces the number of components required and thus reduces the final onChip area. Serializing the system increases the time it takes to compute the output.

Serializing the system means not computing values of the output vector all at the same time, but instead computing group by group, the groups' size are $n_o$. The first output group is computed during $e_0$ and the $i^{th}$ group is computed during $e_i$. The timing of when the outputs are available is found in \cref{tim:serpar}. Those flag control the \ac{CMOS} swicthes present in \cref{circt:xbar}, the switches control which output group is outputed.
